### 2015-09-10 paper.tex
Correct tense
Use PLOS bibstyle
Remove dummy abstract

Lorem ipsum dolor sit amet, consectetur adipiscing elit. Curabitur eget porta
erat. Morbi consectetur est vel gravida pretium. Suspendisse ut dui eu ante
cursus gravida non sed sem. Nullam sapien tellus, commodo id velit id, eleifend
volutpat quam. Phasellus mauris velit, dapibus finibus elementum vel, pulvinar
non tellus. Nunc pellentesque pretium diam, quis maximus dolor faucibus id. Nunc
convallis sodales ante, ut ullamcorper est egestas vitae. Nam sit amet enim
ultrices, ultrices elit pulvinar, volutpat risus.

@@

For each tow, a relevant quasi-steady duration is selected, and then truncated
to include a whole number of blade passages. Over this duration relevant
statistics are calculated.

@@

% Compile your BiBTeX database using our plos2015.bst
% style file and paste the contents of your .bbl file
% here.
% 
\bibliography{library}

>>>>

\todo[inline]{Write abstract.}

@@

For each tow, a relevant quasi-steady duration was selected, and then truncated
to include a whole number of blade passages. Over this duration relevant
statistics are calculated.

@@

% Compile your BiBTeX database using our plos2015.bst
% style file and paste the contents of your .bbl file
% here.
% 
\bibliographystyle{plos2015}
\bibliography{library}
